---
title: "Clean Entries"
author: "Jane Hung"
date: "12 Nov 2020"
output:
    github_document: 
    pandoc_args: --webtex

---

```{r load packages, echo=TRUE, message=FALSE, warning=FALSE}
library(data.table) 
library(gsynth)
library(ggplot2)
library(magrittr)
library(matrixStats)


theme_set(theme_minimal())
knitr::opts_chunk$set(dpi = 300)
```

## Import MTurk Data


```{r cars}
mturk <- fread('../data/mturk_workers.csv')
mturk_subset <- mturk[,c("AssignmentId","WorkerId","AssignmentStatus","AcceptTime","SubmitTime","Answer.surveycode","WorkTimeInSeconds")]
mturk_subset[,duration_min_mturk := as.numeric(WorkTimeInSeconds)/60]
head(mturk_subset)

qualtrics <- fread('../data/qualtrics_results.csv')
# colnames(qualtrics)
qualtrics_subset <-
  qualtrics[, c(
    "StartDate",
    "EndDate",
    "Status" ,
    "IPAddress" ,
    "Progress",
    "Duration (in seconds)",
    "Finished",
    "RecordedDate",
    "ResponseId",
    "Q80",
    "Random ID",
    "FL_6_DO"
  )]

nrow(qualtrics)
# get rid of results from pilot
qualtrics_subset <- qualtrics_subset[63:.N,]
nrow(qualtrics_subset)
setnames(qualtrics_subset,'Q80','WorkerId')
setnames(qualtrics_subset,'Random ID', 'RandomID')
qualtrics_subset[,duration_min := as.numeric(`Duration (in seconds)`)/60]
head(qualtrics_subset)
```

# Find Workers who did not actually answer the survey but submitted a random code

Find people who have the same survey code and verify if they're actually different repsonses
```{r}
table(mturk_subset[,duplicated(WorkerId)])
table(mturk_subset[,duplicated(Answer.surveycode)])
mturk_subset[Answer.surveycode %in% mturk_subset[mturk_subset[,duplicated(Answer.surveycode)]][,Answer.surveycode],]
```

```{r}
qualtrics_subset[WorkerId %in% c('A1CIDX22PNZ73D','A3CEAFFVG5PLF5','A2WP71VTV1F1DV','A2PK7L31SZG0F3'),]
```
Throw out A2WP71VTV1F1DV because can't find their survey results.

Find duplicates on the Qualtrics side.
```{r}
table(qualtrics_subset[,duplicated(WorkerId)])
qualtrics_subset[WorkerId %in% qualtrics_subset[qualtrics_subset[,duplicated(WorkerId)],WorkerId]]
```

```{r}
mturk_subset[WorkerId %in% qualtrics_subset[qualtrics_subset[,duplicated(WorkerId)],WorkerId]]
```
These guys did the survey multiple times but only submitted to Mturk once. Let's see if they used the same survey code elsewhere
```{r}
mturk_subset[Answer.surveycode %in% c("42254", "37684", "72442", "31052", "33364")]

```


Do we have many people who did not take the survey and just entered in a random survey code?
```{r}
length(unique(mturk_subset$WorkerId))
length(unique(qualtrics_subset$WorkerId))

data <- merge(mturk_subset,qualtrics_subset,by='WorkerId',all.x = TRUE)
workers_not_complete <-data[is.na(RandomID),][order(WorkerId)][,WorkerId]
length(workers_not_complete)
workers_not_complete

# This specific worker entered in an additional space by accident
mturk_subset[WorkerId=="AQP4PHYDXRBPI"]
qualtrics_subset[WorkerId=="AQP4PHYDXRBPI "][,WorkerId]
```

There's one person who started the survey and completed the code in MTurk before finishing up the survey.
```{r}
data2 <- merge(mturk_subset,qualtrics_subset,by.x=c('WorkerId','Answer.surveycode'),by.y = c('WorkerId','RandomID'),all.x = TRUE)
workers_not_complete2 <- data2[is.na(Finished),][order(WorkerId)][,WorkerId]
length(workers_not_complete2)
workers_not_complete2[!workers_not_complete2 %in% workers_not_complete]

qualtrics_subset[WorkerId == "A1VJ6JU89HP7MC"]
mturk_subset[WorkerId == "A1VJ6JU89HP7MC"]
```

This Worker does not have matching survey codes, but he sent me a message with the correct survey code.
```{r}
data3 <- merge(mturk_subset,qualtrics_subset,by.x='Answer.surveycode',by.y='RandomID',all.x = TRUE)
workers_not_complete3 <- data3[is.na(WorkerId.y)][order(WorkerId.x)][,WorkerId.x]
# workers_not_complete[!workers_not_complete %in% workers_not_complete3]
workers_not_complete3[!workers_not_complete3 %in% workers_not_complete]

qualtrics_subset[WorkerId=="A1VJ6JU89HP7MC",]
mturk_subset[WorkerId=="A1VJ6JU89HP7MC",]
```

Check to see if there are any survey codes that are more than 6 digits.
```{r}
qualtrics_subset[WorkerId %in% mturk_subset[nchar(Answer.surveycode)>5,WorkerId]]
workers_not_complete4 <- mturk_subset[nchar(Answer.surveycode)>5,][order(WorkerId)][,WorkerId]
workers_not_complete4[!workers_not_complete4 %in% workers_not_complete]
```


# Test survey results that are odd

Testing out duration to see if there are any weird time durations. Let's also see if the duration matches mturk duration.
```{r}
summary(qualtrics_subset$duration_min)
qualtrics_subset[duration_min>13,]
qualtrics_subset[duration_min<6,]
qualtrics_subset[,hist(duration_min,breaks = 20)]

```
```{r}
merge_data <- merge(mturk_subset,qualtrics_subset,by='WorkerId')
merge_data[, time_diff := abs(duration_min - duration_min_mturk)][order(-rank(time_diff))][
  time_diff>2,c("WorkerId","duration_min","duration_min_mturk","time_diff")]
summary(merge_data$time_diff)
hist(merge_data$time_diff)
```
Not removing these for now. Will be a concern for compliance.

Test responses that are all Normal or all Positive. Remove these because they are erroneous.
```{r}
qualtrics_quest <- qualtrics[63:.N, c("Q1",	"Q5",	"Q6",	"Q7",	"Q16",	"Q17",	"Q18",	"Q19",	"Q20",	"Q21",
                                      "Q8",	"Q9",	"Q10",	"Q11",	"Q22"	, "Q23",	"Q24",	"Q25",	"Q26",	"Q27",
                                      "Q12",	"Q13",	"Q14",	"Q15",	"Q28",	"Q29",	"Q30",	"Q31",	"Q32",	"Q33")]

qualtrics_quest[rowSums(qualtrics_quest[,qualtrics_quest=='Normal']) == 30]
qualtrics_quest[rowSums(qualtrics_quest[,qualtrics_quest=='Normal']) == 0]

qualtrics_subset[rowSums(qualtrics_quest[,qualtrics_quest=='Normal']) == 30,][order(WorkerId)][,WorkerId]
qualtrics_subset[rowSums(qualtrics_quest[,qualtrics_quest=='Normal']) == 0,][order(WorkerId)][,WorkerId]

```

```{r}
# for (i in 1:nrow(qualtrics_quest)) {
#   print(qualtrics_quest[1,])
#   rep(c('Normal','Pneumonia'),15)
# }

# qualtrics_quest[,lapply(.SD,function(x) if(x == rep(c('Normal','Pneumonia'),15)) TRUE else FALSE)]
nrow(t(qualtrics_quest))
ncol(t(qualtrics_quest))

data.table(t(qualtrics_quest))[,lapply(.SD,function(x) if(x == rep(c('Normal','Pneumonia'),15)) TRUE else FALSE)]

qualtrics_quest[5,]
```
In the interest of time, just using Google sheets to find this. Normal, Pneumonia alternating
A1W05TSPORJPXR
A3SUWCLD1GEGM7
A3A09JB9X1RBXW
A7VQQEIBSM9IU
A8DER1QY96C5X
A1M8MNKK8H5ZGW
A34D5D6PU193AR

```{r}
qualtrics_subset[Finished=='True',]
```


